Figures

### 2019-05-07 figures/08_exploratory_dotplot.Rmd
explore distributions

# ----
dt_tp_hmap <- dt_sub %>%
  corrr::correlate() %>%
  # corrr::shave() %>%
  # janitor::remove_empty(c("rows", "cols")) %>%
  mutate_if(is.numeric, round, 2) %>%
  data.frame()

@@

@@

>>>>

# ---- heatmap ----
dt_tp_hmap <- dt_sub %>%
  corrr::correlate() %>%
  # corrr::shave() %>%
  # janitor::remove_empty(c("rows", "cols")) %>%
  mutate_if(is.numeric, round, 2) %>%
  data.frame()

@@

# ---- dotplot ----

@@

# ---- densityplots ----
library(ggforce)

ggplot(data = tidyr::gather(dt_sub)) + 
  geom_density(aes(value)) +
  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 1)
ggplot(data = tidyr::gather(dt_sub)) + 
  geom_density(aes(value)) +
  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 2)
ggplot(data = tidyr::gather(dt_sub)) + 
  geom_density(aes(value)) +
  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 3)
ggplot(data = tidyr::gather(dt_sub)) + 
  geom_density(aes(value)) +
  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 4)
